### 2023-01-25 manuscript.tex
latex syntax fun [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/9a7ff254f386b2d4c6b95bea2ca71d9e215395b0.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/9a7ff254f386b2d4c6b95bea2ca71d9e215395b0/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4001755816

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/83ec084ea920c4a2ffc6631608fbfbe21aaa0737/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/83ec084ea920c4a2ffc6631608fbfbe21aaa0737}{stain/2022-fdo-paper@83ec084}
on January 25, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/9a7ff254f386b2d4c6b95bea2ca71d9e215395b0/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/9a7ff254f386b2d4c6b95bea2ca71d9e215395b0}{stain/2022-fdo-paper@9a7ff25}
on January 25, 2023.
